Total Platform Cyber Protection

### 2016-08-23 paper.tex
removed metadata stuff and added dummy dates prediction oct 2016 ;)

% Metadata Information
\acmVolume{9}
\acmNumber{4}
\acmArticle{39}
\acmYear{2010}
\acmMonth{3}

@@

\begin{bottomstuff}
This work is supported by the National Science Foundation, under
grant CNS-0435060, grant CCR-0325197 and grant EN-CS-0329609.

Author's addresses: G. Zhou, Computer Science Department,
College of William and Mary; Y. Wu  {and} J. A. Stankovic,
Computer Science Department, University of Virginia; T. Yan,
Eaton Innovation Center; T. He, Computer Science Department,
University of Minnesota; C. Huang, Google; T. F. Abdelzaher,
(Current address) NASA Ames Research Center, Moffett Field, California 94035.
\end{bottomstuff}

@@

These features of Trojan logic in hardware drive the research that
attempts to detect them.

@@

% History dates
\received{February 2007}{March 2009}{June 2009}

\end{document}
% End of v2-acmsmall-sample.tex (March 2012) - Gerry Murray, ACM

>>>>

% Metadata Information
%\acmVolume{9}
%\acmNumber{4}
\acmArticle{37}
\acmYear{2016}
\acmMonth{10}

@@

\begin{bottomstuff}
	Need to add stuff here
\end{bottomstuff}

@@

% TODO Sai: What features??
These features of Trojan logic in hardware drive the research that
attempts to detect them.

@@

% History dates
\received{September 2016}{October 2016}{October 2016}

\end{document}
